cardinalR: Generating Interesting High-Dimensional Data Structures

### 2025-12-15 paper-cardinalR.Rmd
Started updating projections

```{r orglinearbranches-proj1}
scaled_data <- scale_data_manual(orglinearbranches)

@@

proj_obj1 <- get_projection(projection = projection, 
                            proj_scale = 1.8, 
                            scaled_data = scaled_data, 
                            axis_param = list(limits = 0.15,
                                              axis_scaled = 10, 
                                              axis_pos_x = -0.12, 
                                              axis_pos_y = -0.12, 
                                              threshold = 0.015))

@@

proj_obj2 <- get_projection(projection = projection, 
                            proj_scale = 1.2, 
                            scaled_data = scaled_data, 
                            axis_param = list(limits = 0.7,
                                              axis_scaled = 3, 
                                              axis_pos_x = -0.57, 
                                              axis_pos_y = -0.57, 
                                              threshold = 0.01))

@@

proj_obj3 <- get_projection(projection = projection, 
                            proj_scale = 1.2, 
                            scaled_data = scaled_data, 
                            axis_param = list(limits = 0.6,
                                              axis_scaled = 1.5, 
                                              axis_pos_x = -0.4, 
                                              axis_pos_y = -0.4, 
                                              threshold = 0.016))

@@

```{r cone-proj1}
scaled_data <- scale_data_manual(cone)

@@

proj_obj1 <- get_projection(projection = projection, 
                            proj_scale = 1.2, 
                            scaled_data = scaled_data, 
                            axis_param = list(limits = 0.25,
                                              axis_scaled = 3, 
                                              axis_pos_x = -0.2, 
                                              axis_pos_y = -0.2, 
                                              threshold = 0.022))

@@

proj_obj2 <- get_projection(projection = projection, 
                            proj_scale = 1.2, 
                            scaled_data = scaled_data, 
                            axis_param = list(limits = 0.1,
                                              axis_scaled = 3, 
                                              axis_pos_x = -0.08, 
                                              axis_pos_y = -0.08, 
                                              threshold = 0.01))

@@

proj_obj3 <- get_projection(projection = projection, 
                            proj_scale = 1.2, 
                            scaled_data = scaled_data, 
                            axis_param = list(limits = 0.25,
                                              axis_scaled = 3, 
                                              axis_pos_x = -0.25, 
                                              axis_pos_y = -0.25, 
                                              threshold = 0.016))

@@

```{r pyrrect-proj1}
scaled_data <- scale_data_manual(pyrrect)

@@

proj_obj1 <- get_projection(projection = projection, 
                            proj_scale = 1.2, 
                            scaled_data = scaled_data, 
                            axis_param = list(limits = 0.7,
                                              axis_scaled = 1.2, 
                                              axis_pos_x = -0.5, 
                                              axis_pos_y = -0.5, 
                                              threshold = 0.022))

@@

proj_obj2 <- get_projection(projection = projection, 
                            proj_scale = 1.2, 
                            scaled_data = scaled_data, 
                            axis_param = list(limits = 0.7,
                                              axis_scaled = 1.7, 
                                              axis_pos_x = -0.45, 
                                              axis_pos_y = -0.45, 
                                              threshold = 0.08))

@@

```{r pyrtri-proj1}
scaled_data <- scale_data_manual(pyrtri)

@@

proj_obj1 <- get_projection(projection = projection, 
                            proj_scale = 1.2, 
                            scaled_data = scaled_data, 
                            axis_param = list(limits = 0.3,
                                              axis_scaled = 1.2, 
                                              axis_pos_x = -0.2, 
                                              axis_pos_y = -0.2, 
                                              threshold = 0.022))

@@

proj_obj2 <- get_projection(projection = projection, 
                            proj_scale = 1.2, 
                            scaled_data = scaled_data, 
                            axis_param = list(limits = 0.3,
                                              axis_scaled = 1.5, 
                                              axis_pos_x = -0.25, 
                                              axis_pos_y = -0.25, 
                                              threshold = 0.03))

@@

```{r pyrstar-proj1}
scaled_data <- scale_data_manual(pyrstar)

@@

proj_obj3 <- get_projection(projection = projection, 
                            proj_scale = 1.2, 
                            scaled_data = scaled_data, 
                            axis_param = list(limits = 0.6,
                                              axis_scaled = 1.5, 
                                              axis_pos_x = -0.6, 
                                              axis_pos_y = -0.6, 
                                              threshold = 0.016))

@@

```{r pyrholes-proj1}
scaled_data <- scale_data_manual(pyrholes)

@@

```{r circle-proj1}
scaled_data <- scale_data_manual(circle)

@@

proj_obj1 <- get_projection(projection = projection, 
                            proj_scale = 1.2, 
                            scaled_data = scaled_data, 
                            axis_param = list(limits = 0.7,
                                              axis_scaled = 1.2, 
                                              axis_pos_x = -0.6, 
                                              axis_pos_y = -0.6, 
                                              threshold = 0.022))

@@

proj_obj3 <- get_projection(projection = projection, 
                            proj_scale = 1.2, 
                            scaled_data = scaled_data, 
                            axis_param = list(limits = 0.6,
                                              axis_scaled = 1.5, 
                                              axis_pos_x = -0.5, 
                                              axis_pos_y = -0.5, 
                                              threshold = 0.016))

@@

```{r curvycycle-proj1}
scaled_data <- scale_data_manual(curvycycle)

@@

proj_obj2 <- get_projection(projection = projection, 
                            proj_scale = 1.2, 
                            scaled_data = scaled_data, 
                            axis_param = list(limits = 0.7,
                                              axis_scaled = 1.5, 
                                              axis_pos_x = -0.57, 
                                              axis_pos_y = -0.57, 
                                              threshold = 0.04))

@@

```{r clusteredspheres-proj1}
scaled_data <- scale_data_manual(clusteredspheres)

@@

proj_obj2 <- get_projection(projection = projection, 
                            proj_scale = 1.2, 
                            scaled_data = scaled_data, 
                            axis_param = list(limits = 0.7,
                                              axis_scaled = 1, 
                                              axis_pos_x = -0.57, 
                                              axis_pos_y = -0.57, 
                                              threshold = 0.01))

@@

```{r trefoil4d-proj1}
scaled_data <- scale_data_manual(trefoil4d)

@@

proj_obj3 <- get_projection(projection = projection, 
                            proj_scale = 1.2, 
                            scaled_data = scaled_data, 
                            axis_param = list(limits = 0.7,
                                              axis_scaled = 1.5, 
                                              axis_pos_x = -0.55, 
                                              axis_pos_y = -0.55, 
                                              threshold = 0.016))

@@

```{r trefoil3d-proj1}
scaled_data <- scale_data_manual(trefoil3d)

@@

```{r curvycylinder-proj1}
scaled_data <- scale_data_manual(curvycylinder)

@@

```{r sphericalspiral-proj1}
scaled_data <- scale_data_manual(sphericalspiral)

@@

```{r conicspiral-proj1}
scaled_data <- scale_data_manual(conicspiral)

@@

proj_obj2 <- get_projection(projection = projection, 
                            proj_scale = 1.2, 
                            scaled_data = scaled_data, 
                            axis_param = list(limits = 0.7,
                                              axis_scaled = 3, 
                                              axis_pos_x = -0.65, 
                                              axis_pos_y = -0.65, 
                                              threshold = 0.01))

@@

proj_obj3 <- get_projection(projection = projection, 
                            proj_scale = 1.2, 
                            scaled_data = scaled_data, 
                            axis_param = list(limits = 0.6,
                                              axis_scaled = 1.5, 
                                              axis_pos_x = -0.45, 
                                              axis_pos_y = -0.45, 
                                              threshold = 0.016))

@@

```{r nonlinear-proj1}
scaled_data <- scale_data_manual(nonlinear)

@@

proj_obj1 <- get_projection(projection = projection, 
                            proj_scale = 1.2, 
                            scaled_data = scaled_data, 
                            axis_param = list(limits = 0.7,
                                              axis_scaled = 1.2, 
                                              axis_pos_x = -0.3, 
                                              axis_pos_y = -0.3, 
                                              threshold = 0.022))

@@

proj_obj2 <- get_projection(projection = projection, 
                            proj_scale = 1.2, 
                            scaled_data = scaled_data, 
                            axis_param = list(limits = 0.45,
                                              axis_scaled = 1.3, 
                                              axis_pos_x = -0.2, 
                                              axis_pos_y = -0.2, 
                                              threshold = 0.03))

@@

proj_obj3 <- get_projection(projection = projection, 
                            proj_scale = 1.2, 
                            scaled_data = scaled_data, 
                            axis_param = list(limits = 0.45,
                                              axis_scaled = 1.5, 
                                              axis_pos_x = -0.25, 
                                              axis_pos_y = -0.25, 
                                              threshold = 0.016))

@@

```{r five-clusts-projections1}
scaled_data <- scale_data_manual(five_clusts[, -5])

@@

proj_obj1 <- get_projection(projection = projection, 
                            proj_scale = 1.23, 
                            scaled_data = scaled_data, 
                            axis_param = list(limits = 1,
                                              axis_scaled = 0.8, 
                                              axis_pos_x = -0.9, 
                                              axis_pos_y = -0.9, 
                                              threshold = 0.05))

@@

proj_obj2 <- get_projection(projection = projection, 
                            proj_scale = 1.23, 
                            scaled_data = scaled_data, 
                            axis_param = list(limits = 1,
                                              axis_scaled = 0.8, 
                                              axis_pos_x = -0.9, 
                                              axis_pos_y = -0.9, 
                                              threshold = 0.07))

@@

proj_obj3 <- get_projection(projection = projection, 
                            proj_scale = 1.23, 
                            scaled_data = scaled_data, 
                            axis_param = list(limits = 1,
                                              axis_scaled = 0.8, 
                                              axis_pos_x = -0.9, 
                                              axis_pos_y = -0.9, 
                                              threshold = 0.05))

@@

```{r five-4clusts-projections1}
scaled_data <- scale_data_manual(five_clusts[, -5])

@@

```{r five-5clusts-projections1}
scaled_data <- scale_data_manual(five_clusts[, -5])

>>>>

```{r orglinearbranches-proj1}
centered_data <- center_data(orglinearbranches)

@@

proj_obj1 <- get_projection(projection = projection, 
                            proj_scale = 1.8, 
                            centered_data = centered_data, 
                            axis_param = list(limits = 0.15,
                                              axis_scaled = 10, 
                                              axis_pos_x = -0.12, 
                                              axis_pos_y = -0.12, 
                                              threshold = 0.015))

@@

proj_obj2 <- get_projection(projection = projection, 
                            proj_scale = 1.2, 
                            centered_data = centered_data, 
                            axis_param = list(limits = 0.7,
                                              axis_scaled = 3, 
                                              axis_pos_x = -0.57, 
                                              axis_pos_y = -0.57, 
                                              threshold = 0.01))

@@

proj_obj3 <- get_projection(projection = projection, 
                            proj_scale = 1.2, 
                            centered_data = centered_data, 
                            axis_param = list(limits = 0.6,
                                              axis_scaled = 1.5, 
                                              axis_pos_x = -0.4, 
                                              axis_pos_y = -0.4, 
                                              threshold = 0.016))

@@

```{r cone-proj1}
centered_data <- center_data(cone)

@@

proj_obj1 <- get_projection(projection = projection, 
                            proj_scale = 1.2, 
                            centered_data = centered_data, 
                            axis_param = list(limits = 0.25,
                                              axis_scaled = 3, 
                                              axis_pos_x = -0.2, 
                                              axis_pos_y = -0.2, 
                                              threshold = 0.022))

@@

proj_obj2 <- get_projection(projection = projection, 
                            proj_scale = 1.2, 
                            centered_data = centered_data, 
                            axis_param = list(limits = 0.1,
                                              axis_scaled = 3, 
                                              axis_pos_x = -0.08, 
                                              axis_pos_y = -0.08, 
                                              threshold = 0.01))

@@

proj_obj3 <- get_projection(projection = projection, 
                            proj_scale = 1.2, 
                            centered_data = centered_data, 
                            axis_param = list(limits = 0.25,
                                              axis_scaled = 3, 
                                              axis_pos_x = -0.25, 
                                              axis_pos_y = -0.25, 
                                              threshold = 0.016))

@@

```{r pyrrect-proj1}
centered_data <- center_data(pyrrect)

@@

proj_obj1 <- get_projection(projection = projection, 
                            proj_scale = 1.2, 
                            centered_data = centered_data, 
                            axis_param = list(limits = 0.7,
                                              axis_scaled = 1.2, 
                                              axis_pos_x = -0.5, 
                                              axis_pos_y = -0.5, 
                                              threshold = 0.022))

@@

proj_obj2 <- get_projection(projection = projection, 
                            proj_scale = 1.2, 
                            centered_data = centered_data, 
                            axis_param = list(limits = 0.7,
                                              axis_scaled = 1.7, 
                                              axis_pos_x = -0.45, 
                                              axis_pos_y = -0.45, 
                                              threshold = 0.08))

@@

```{r pyrtri-proj1}
centered_data <- center_data(pyrtri)

@@

proj_obj1 <- get_projection(projection = projection, 
                            proj_scale = 1.2, 
                            centered_data = centered_data, 
                            axis_param = list(limits = 0.3,
                                              axis_scaled = 1.2, 
                                              axis_pos_x = -0.2, 
                                              axis_pos_y = -0.2, 
                                              threshold = 0.022))

@@

proj_obj2 <- get_projection(projection = projection, 
                            proj_scale = 1.2, 
                            centered_data = centered_data, 
                            axis_param = list(limits = 0.3,
                                              axis_scaled = 1.5, 
                                              axis_pos_x = -0.25, 
                                              axis_pos_y = -0.25, 
                                              threshold = 0.03))

@@

```{r pyrstar-proj1}
centered_data <- center_data(pyrstar)

@@

proj_obj3 <- get_projection(projection = projection, 
                            proj_scale = 1.2, 
                            centered_data = centered_data, 
                            axis_param = list(limits = 0.6,
                                              axis_scaled = 1.5, 
                                              axis_pos_x = -0.6, 
                                              axis_pos_y = -0.6, 
                                              threshold = 0.016))

@@

```{r pyrholes-proj1}
centered_data <- center_data(pyrholes)

@@

```{r circle-proj1}
centered_data <- center_data(circle)

@@

proj_obj1 <- get_projection(projection = projection, 
                            proj_scale = 1.2, 
                            centered_data = centered_data, 
                            axis_param = list(limits = 0.7,
                                              axis_scaled = 1.2, 
                                              axis_pos_x = -0.6, 
                                              axis_pos_y = -0.6, 
                                              threshold = 0.022))

@@

proj_obj3 <- get_projection(projection = projection, 
                            proj_scale = 1.2, 
                            centered_data = centered_data, 
                            axis_param = list(limits = 0.6,
                                              axis_scaled = 1.5, 
                                              axis_pos_x = -0.5, 
                                              axis_pos_y = -0.5, 
                                              threshold = 0.016))

@@

```{r curvycycle-proj1}
centered_data <- center_data(curvycycle)

@@

proj_obj2 <- get_projection(projection = projection, 
                            proj_scale = 1.2, 
                            centered_data = centered_data, 
                            axis_param = list(limits = 0.7,
                                              axis_scaled = 1.5, 
                                              axis_pos_x = -0.57, 
                                              axis_pos_y = -0.57, 
                                              threshold = 0.04))

@@

```{r clusteredspheres-proj1}
centered_data <- center_data(clusteredspheres)

@@

proj_obj2 <- get_projection(projection = projection, 
                            proj_scale = 1.2, 
                            centered_data = centered_data, 
                            axis_param = list(limits = 0.7,
                                              axis_scaled = 1, 
                                              axis_pos_x = -0.57, 
                                              axis_pos_y = -0.57, 
                                              threshold = 0.01))

@@

```{r trefoil4d-proj1}
centered_data <- center_data(trefoil4d)

@@

proj_obj3 <- get_projection(projection = projection, 
                            proj_scale = 1.2, 
                            centered_data = centered_data, 
                            axis_param = list(limits = 0.7,
                                              axis_scaled = 1.5, 
                                              axis_pos_x = -0.55, 
                                              axis_pos_y = -0.55, 
                                              threshold = 0.016))

@@

```{r trefoil3d-proj1}
centered_data <- center_data(trefoil3d)

@@

```{r curvycylinder-proj1}
centered_data <- center_data(curvycylinder)

@@

```{r sphericalspiral-proj1}
centered_data <- center_data(sphericalspiral)

@@

```{r conicspiral-proj1}
centered_data <- center_data(conicspiral)

@@

proj_obj2 <- get_projection(projection = projection, 
                            proj_scale = 1.2, 
                            centered_data = centered_data, 
                            axis_param = list(limits = 0.7,
                                              axis_scaled = 3, 
                                              axis_pos_x = -0.65, 
                                              axis_pos_y = -0.65, 
                                              threshold = 0.01))

@@

proj_obj3 <- get_projection(projection = projection, 
                            proj_scale = 1.2, 
                            centered_data = centered_data, 
                            axis_param = list(limits = 0.6,
                                              axis_scaled = 1.5, 
                                              axis_pos_x = -0.45, 
                                              axis_pos_y = -0.45, 
                                              threshold = 0.016))

@@

```{r nonlinear-proj1}
centered_data <- center_data(nonlinear)

@@

proj_obj1 <- get_projection(projection = projection, 
                            proj_scale = 1.2, 
                            centered_data = centered_data, 
                            axis_param = list(limits = 0.7,
                                              axis_scaled = 1.2, 
                                              axis_pos_x = -0.3, 
                                              axis_pos_y = -0.3, 
                                              threshold = 0.022))

@@

proj_obj2 <- get_projection(projection = projection, 
                            proj_scale = 1.2, 
                            centered_data = centered_data, 
                            axis_param = list(limits = 0.45,
                                              axis_scaled = 1.3, 
                                              axis_pos_x = -0.2, 
                                              axis_pos_y = -0.2, 
                                              threshold = 0.03))

@@

proj_obj3 <- get_projection(projection = projection, 
                            proj_scale = 1.2, 
                            centered_data = centered_data, 
                            axis_param = list(limits = 0.45,
                                              axis_scaled = 1.5, 
                                              axis_pos_x = -0.25, 
                                              axis_pos_y = -0.25, 
                                              threshold = 0.016))

@@

```{r five-clusts-projections1}
centered_data <- center_data(five_clusts[, -5])

@@

proj_obj1 <- get_projection(projection = projection, 
                            proj_scale = 1.23, 
                            centered_data = centered_data, 
                            axis_param = list(limits = 1,
                                              axis_scaled = 0.8, 
                                              axis_pos_x = -0.9, 
                                              axis_pos_y = -0.9, 
                                              threshold = 0.05))

@@

proj_obj2 <- get_projection(projection = projection, 
                            proj_scale = 1.23, 
                            centered_data = centered_data, 
                            axis_param = list(limits = 1,
                                              axis_scaled = 0.8, 
                                              axis_pos_x = -0.9, 
                                              axis_pos_y = -0.9, 
                                              threshold = 0.07))

@@

proj_obj3 <- get_projection(projection = projection, 
                            proj_scale = 1.23, 
                            centered_data = centered_data, 
                            axis_param = list(limits = 1,
                                              axis_scaled = 0.8, 
                                              axis_pos_x = -0.9, 
                                              axis_pos_y = -0.9, 
                                              threshold = 0.05))

@@

```{r five-4clusts-projections1}
centered_data <- center_data(five_clusts[, -5])

@@

```{r five-5clusts-projections1}
centered_data <- center_data(five_clusts[, -5])
